I can see clearly now: reinterpreting statistical significance

### 2019-01-09 doc.tex
A bit more fiddling; I would like to hand off.

Changing from ``significance'' to ``clarity'' should help researchers improve their statistical practice, but of course it cannot solve all of our problems with statistics. \bmb{repetitive with \P 3 of Conclusion?}The idea of ``statistical clarity'' will work best if it remains linked to the principles of attaching clarity to the study, rather than the system, and of focusing on effects and confidence intervals. If widely adopted, ``statistical clarity'' could eventually come to be seen as an end in itself, the way that ``significance'' is now; similarly, ``statistical clarity'' could be confounded with other meanings of  ``clarity'' as ``significance'' is now. We hope not, but in any case we feel that the unthinking use of ``clarity'' would be (marginally) better than the current unthinking use of ``significance''. We have found that scientists' understanding of our proposed use of statistical clarity is enhanced by explicitly connecting clarity statements to statements about P values.

>>>>

Changing from ``significance'' to ``clarity'' should help researchers improve their statistical practice, but of course it cannot solve all of our problems with statistics. \bmb{repetitive with \P 3 of Conclusion?} The idea of ``statistical clarity'' will work best if it remains linked to the principles of attaching clarity to the study, rather than the system, and of focusing on effects and confidence intervals. If widely adopted, ``statistical clarity'' could eventually come to be seen as an end in itself, the way that ``significance'' is now. We hope not, but in we feel that the unthinking use of ``clarity'' would be (marginally) better than the current unthinking use of ``significance''. If there is a transition it will also be important to communicate clearly when ``clarity'' is being used in a technical sense; we have found that in particular that understanding is improved by explicitly connecting clarity statements to statements about P values.
